---
title: "A02b_G33821119"
author: "LM"
date: "1/27/2018"
output: html_document
---
Part A
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install tidyverse package.

```{r }
#install.packages("tidyverse")
library(tidyverse)
```

## read the file

```{r }
households<-read_csv(file = "/Users/malaisi/Desktop/programming analytics/households.csv")

```

part a(a).
Categorical variables:  Location, Ownership,Household
Continuous variables: First Income, Second Income, Monthly Payment,Utilities, Debt.

part a(b).
All the variables in the categorical variables in this data frame are nominal variables.

part a(c).
```{r }
 
 hist(households$Debt,col="light green",main="Debt Histogram", ylab="Amount",xlab="Debt",breaks=200)

```



it is like a symmetric distribution, and most of the debt are between 1700-7000.



part a(d).
```{r}
sprintf("The maximum debt level for the households: %s", max(households$Debt))#to print the maximum debt level
sprintf("The minimux debt level for the households: %s", min(households$Debt))# to print the minimum debt level
```

part a(e).
```{r}
sprintf("Indebtedness levels at 25th percentiles: %s", quantile(households$Debt,.25))
sprintf("Indebtedness levels at 50th percentiles: %s", quantile(households$Debt,.50))
sprintf("Indebtedness levels at 75th percentiles: %s", quantile(households$Debt,.75))

```

part a(f).
```{r}
sprintf("interquartile range for the indebtedness levels of households is: %s", IQR(households$Debt))

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
